Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-25 SRO_Retest_Analyses.Rmd
cont working on retest exploration

---
title: 'Self Regulation Ontology Retest Data: Initial Exploration'
output:
  html_notebook: default
  pdf_document: default
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

@@

Data cleaning for efa
```{r}
#read in only meaningful vars
meaningful_var_test <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_clean.csv')

@@

Checking columns for efa:
NEED TO RESOLVE SOME DIFFERENCES IN MEANINGFUL VARS BETWEEN THE TWO DATASETS
```{r}
#Check columns 
names(retest_data_mngf)[names(retest_data_mngf) %in% names(retest_subs_test_mngf) == FALSE]

@@

Efa on subjects from original dataset withOUT retest data (using meaningful vars only)
```{r}
unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")

@@

```{r}
corMat <- rest_subs_test_mngf_z %>% select(-sub_id) %>% cor(.,use = 'complete.obs')

@@

```{r}
solution
```

>>>>

---
title: 'Self Regulation Ontology Retest Data: Initial Exploration'
output:
  html_document:
    toc: yes
    toc_float: yes
---

@@

Data cleaning for efa
```{r eval=FALSE}
#read in only meaningful vars
meaningful_var_test <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_clean.csv')

@@

Checking columns for efa:
NEED TO RESOLVE SOME DIFFERENCES IN MEANINGFUL VARS BETWEEN THE TWO DATASETS
```{r eval=FALSE}
#Check columns 
names(retest_data_mngf)[names(retest_data_mngf) %in% names(retest_subs_test_mngf) == FALSE]

@@

Efa on subjects from original dataset withOUT retest data (using meaningful vars only)
```{r eval=FALSE}
unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")

@@

```{r eval = FALSE}
corMat <- rest_subs_test_mngf_z %>% select(-sub_id) %>% cor(.,use = 'complete.obs')

@@

```{r eval = FALSE}
solution
```
